Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-16 manuscript.tex
Add files via upload
went through the paper, updated slopes in table A.1 and fixed minor typos

\umberto{For each of the 4500 simulations considered, Eq. \ref{eq:RV:correction.overall} was applied. The use of Eq. \ref{eq:RV:correction.overall} leads to some additional comments. First of all we note that both the function that corrects for stellar activity and the keplerian signal must be simultaneously considered, as shown in Sec. \ref{sec:soap.spot.planet}. Because of the non linearity of the model that defines the orbital parameters of the exoplanets, non linear least squares \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear} must be used. In order to run the algorithm, a set of initial values for the parameters of interest has to be provided. Concerning the parameters related to the activity correction, we have chosen as initial values the ones obtained by only considering Eq.~\ref{eq:RV:correction}. The selection of the initial values for the orbital parameters of the exoplanet is more challenging. In the present study we assumed the circularity of the orbit, hence the parameters to estimate are the amplitude $K$, the epoch at the periapsis $t_0$ and the orbital period $P$. As initial value for $K$ we selected the maximum measured RV. The epoch at the periapsis $t_0$ is defined as that epoch such that the distance between the planet and the star is the smallest. Since in our simulation study the orbit of the planet in circular, the distance star--planet does not change over time, making the choice for $t_0$ arbitrary. We selected as initial value for $t_0$ that epoch for which the largest RV was measured. When providing an initial value for the orbital period $P$, we note that an initial value far from the true one can result in the non linear least squares algorithm to get stuck in local modes  \citep[][]{levenberg1944method,marquardt1963algorithm}, providing a wrong set of estimates for all the parameters of Eq. \ref{eq:RV:correction.overall} We note that in  Sec. \ref{sec:soap.spot.planet}, because the amplitude was equal to $K=10 \ms$, a good initial guess for the orbital period was available and local modes were avoided. For this reason we selected as initial guess for $P$ a value close to the true orbital period. This simplification is motivated by the fact that we are mainly interested in evaluating the goodness of the activity correction function presented in Eq.~\ref{eq:RV:correction} respect to the usual one, based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit. In order to properly do that, we need to correctly estimating the orbital parameters of the exoplanets as well. Because of the challenges related to the non linearity of the keplerian signal, we assumed to have a good initial guess for the orbital period. However, how to correctly estimating the orbital parameters of the extrasolar planet, in particular when no assumption on the eccentricity of the orbit are available, is something to investigate in future analyses.

>>>>

\umberto{For each of the 4500 simulations considered, Eq. \ref{eq:RV:correction.overall} was applied. The use of Eq. \ref{eq:RV:correction.overall} leads to some additional comments. First of all we note that both the function that corrects for stellar activity and the keplerian signal must be simultaneously considered, as shown in Sec. \ref{sec:soap.spot.planet}. Because of the non linearity of the model that defines the orbital parameters of the exoplanets, non linear least squares \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear} must be used. In order to run the algorithm, a set of initial values for the parameters of interest has to be provided. Concerning the parameters related to the activity correction, we have chosen as initial values the ones obtained by only considering Eq.~\ref{eq:RV:correction}. The selection of the initial values for the orbital parameters of the exoplanet is more challenging. In the present study we assumed the circularity of the orbit, hence the parameters to estimate are the amplitude $K$, the epoch at the periapsis $t_0$ and the orbital period $P$. As initial value for $K$ we selected the maximum measured RV. The epoch at the periapsis $t_0$ is defined as that epoch such that the distance between the planet and the star is the smallest. Since in our simulation study the orbit of the planet in circular, the distance star--planet does not change over time, making the choice for $t_0$ arbitrary. We selected as initial value for $t_0$ that epoch for which the largest RV was measured. When providing an initial value for the orbital period $P$, we note that an initial value far from the true one can result in the non linear least squares algorithm to get stuck in local modes  \citep[][]{levenberg1944method,marquardt1963algorithm}, providing a wrong set of estimates for all the parameters of Eq. \ref{eq:RV:correction.overall} We note that in Sec. \ref{sec:soap.spot.planet}, because the semi-amplitude of the injected exoplanet was equal to 10 \ms, a good initial guess for the orbital period was available and local modes were avoided. For this reason we selected as initial guess for $P$ a value close to the true orbital period. This simplification is motivated by the fact that we are mainly interested in evaluating the goodness of the activity correction function presented in Eq.~\ref{eq:RV:correction} respect to the usual one, based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit. In order to properly do that, we need to correctly estimating the orbital parameters of the exoplanets as well. Because of the challenges related to the non linearity of the keplerian signal, we assumed to have a good initial guess for the orbital period. However, how to correctly estimating the orbital parameters of the extrasolar planet, in particular when no assumption on the eccentricity of the orbit are available, is something to investigate in future analyses.
